Visual Diagnostics for Constrained Optimisation with Application to Guided Tours

### 2022-01-05 paper/zhang-cook-laa-langrene-menendez.tex
final clean up

Variables \texttt{x1}, \texttt{x8} to \texttt{x10} are normal noise with
zero mean, and unit variance and \texttt{x2} to \texttt{x7} are normal
mixtures with varied weights and locations. All the variables have been
scaled to have overall unit variance before projection pursuit. The
holes index \citep{cook2008grand}, used for detecting bimodality of the
variables, is used throughout the examples unless otherwise specified.

>>>>

\noindent Variables \texttt{x1}, \texttt{x8} to \texttt{x10} are normal
noise with zero mean, and unit variance and \texttt{x2} to \texttt{x7}
are normal mixtures with varied weights and locations. All the variables
have been scaled to have overall unit variance before projection
pursuit. The holes index \citep{cook2008grand}, used for detecting
bimodality of the variables, is used throughout the examples unless
otherwise specified.
